Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-07-05 answer-to-reviewers.tex

This is expected as the general task considered by the authors is probably NP-hard (e.g. it should be possible to map it somehow to an inference in a credal network, see for instance Maua' et al., JAIR 2014). Yet, I miss a deeper discussion about the values of the parameters of the problem for which a brute-force computation of $\tilde{n}$ in Eq. 10 can be avoided. The authors say that this is the case in the 'vast majority' of the time points, but this is a strong claim, which deserves a discussion.

Of course, the discussion in S6.2 and the examples in S7 are doing something in this direction, but this is not enough.

A theoretical or empirical analysis should be necessarily added to convince the reader about the practical applicability of the result.
An idea might be a non-brute-force, approximate, approach (e.g., some sampling-based inner approximation). In the discrete case, such sampling can be drastically improved by sampling only on the extreme distribution (of the convex credal sets). This is less straightforward with continuous parameter, but it should be possible to do something even in this case (and I guess some paper by Alessio Benavoli can give direction about that).

\medskip
\emph{We have added just under 3 pages of analysis with detailed graphical plots on the question of how often one has to resort to numerical optimisation in Appendix~B in a manner that should be useful in illuminating the practical applicability of the method for readers interested in applying it.
We also reran the automotive brake example and measured precisely how often the theory helps for the automotive brake example in Section~7.2.2, adding a short comment in place and more detail in the same Appendix.}

\medskip

@@

- Sec 4, why not to cite that the re-parametrization is based on the re-parametrization a' la Walley for the Dir distribution?

\medskip
\emph{Agreed. This parametrization for conjugate priors in exponential families has been known for a long time
(see, e.g., Diaconis \& Ylvisaker 1979),
but Walley (1991, \S 5.3) showed its usefulness for the imprecise Beta model, and then for the IDM.
}
\medskip

- I would shape the example at the end of S4 in an example environment

\medskip
\emph{As we have our main examples in Section~7 in a separate subsection,
putting the example at the end of Section~4 in an example environment would be awkward as
it would remain the sole example formatted in that way.}
\medskip

### 2016-07-05 ijar-npb-ms.tex
different colours for figures B.12 and B.13, rewriting appendix B.3, and minor tweaks

In Section \ref{sec:survsign} we review the survival 
signature and in Section \ref{sec:nonparamapproach} we 
review the nonparametric approach to Bayesian reliability analysis
upon which our work builds 
\cite{2015:bayessurvsign}.  Section \ref{sec:reparam} details
the reparameterisation of that approach which enables the natural
formulation of the system reliability bounds, leading to
nice closed form results in some later theory.
Section \ref{sec:setsofbetapriors} lays the ground work to incorporate imprecise probability,
culminating in the main results and contributions of this 
work, detailed in Section \ref{sec:setsofrel}.  Section 
\ref{sec:examples} provides details on the software contributions
of this work and shows two worked examples
demonstrating the practicality and usefulness of the method.

@@

In this example, the theory presented in Section \ref{sec:setsofrel} enabled avoiding numerical optimisation
in 91.9\% of cases for $\lRsys(\cdot)$ and in 95.7\% of cases for $\uRsys(\cdot)$.
Further detail is in Appendix \ref{ap:needtoopt}.

@@

Given some unknown functioning probability $p$, which gives rise to the observed data $s$, the probability that Theorem 1 does not apply is
\begin{align*}
  &P(y(N+m-1)-m+1 < s < y(N+m-1)) \\
  &\qquad \qquad \qquad \qquad = \sum_{i = \lceil y(N+m-1)-m+1 \rceil}^{\lfloor y(N+m-1) \rfloor} \binom{N}{i} p^i (1-p)^{N-i}
\end{align*}
Likewise the probability that Lemma 3 does not apply is
\begin{align*}
  &P(\mathcal{L}_{\nu,\nl}(0) \lesseqgtr 1 \cap \mathcal{L}_{\nu,\nl}(m) \gtreqless 1) = \sum_{s \in \mathcal{S}} \binom{N}{s} p^s (1-p)^{N-s} \\
  &\qquad\mbox{where}\quad \mathcal{S} = \left\{ s : \frac{p(0 \mid y, \nu, m, s, N)}{p(0 \mid y, \nl, m, s, N)} \lesseqgtr 1 \cap \frac{p(m \mid y, \nu, m, s, N)}{p(m \mid y, \nl, m, s, N)} \gtreqless 1 \right\}
\end{align*}

@@

Note that all these analyses are for evaluation of a single fixed time point at which $\lRsys(\cdot)$ or $\uRsys(\cdot)$ is computed.  Of relevance to the overall compute time is the behaviour over time, so that seems unlikely that the worst case scenario will occur for long runs of the times under analysis.

\subsection{Theoretical analysis for brake system example}

By way of example, a temporal analysis of the constrained worst case analysis is now presented for the real example in Section \ref{sec:brakeex}.

Figure \ref{fig:need-to-opt-8} shows the changing worst case probability (subject to $|y-p|>0.1$) that optimisation will be required over time for the actual choice of prior and the values of $m, N, \nu$ and $\nl$ in the brake example from the main body of the paper.  Note in particular that when $m=1$, Lemma 3 always applies for $y \in (0,1)$ and so optimisation is never required.  This is true for all values of $N$ and $y$.

@@

As explained in section \ref{sec:brakeex}, the grid contained 301 time points and the system has 4 types of component, meaning a stochastic dominance must be verified via theory or optimisation $1,204$ times for each of $\lRsys(\cdot)$ and $\uRsys(\cdot)$.  In total, theory could not determine stochastic dominance in 98 (or 8.1\%) of cases for $\lRsys(\cdot)$, while it was in 52 (or 4.3\%) of cases for $\uRsys(\cdot)$.

>>>>

In Section \ref{sec:survsign} we review the survival 
signature and in Section \ref{sec:nonparamapproach} we 
review the nonparametric approach to Bayesian reliability analysis
upon which our work builds 
\cite{2015:bayessurvsign}.  Section \ref{sec:reparam} details
the reparametrisation of that approach which enables the natural
formulation of the system reliability bounds, leading to
nice closed form results in some later theory.
Section \ref{sec:setsofbetapriors} lays the ground work to incorporate imprecise probability,
culminating in the main results and contributions of this 
work, detailed in Section \ref{sec:setsofrel}.  Section 
\ref{sec:examples} provides details on the software contributions
of this work and shows two worked examples
demonstrating the practicality and usefulness of the method.

@@

In this example, the theory presented in Section \ref{sec:setsofrel} enabled avoiding numerical optimisation
in 91.9\% of cases for $\lRsys(\cdot)$ and in 95.7\% of cases for $\uRsys(\cdot)$.
Further detail is in Appendix \ref{ap:needtoopt-brake}.

@@

Given some unknown functioning probability $p$, which gives rise to the observed data $s$, the probability that Theorem~2 does not apply is
\begin{align*}
  &P(y(N+m-1)-m+1 < s < y(N+m-1)) \\
  &\qquad \qquad \qquad \qquad = \sum_{i = \lceil y(N+m-1)-m+1 \rceil}^{\lfloor y(N+m-1) \rfloor} \binom{N}{i} p^i (1-p)^{N-i}
\end{align*}
Likewise the probability that Lemma~3 does not apply is
\begin{align*}
  &P(\mathcal{L}_{\nu,\nl}(0) \lesseqgtr 1 \cap \mathcal{L}_{\nu,\nl}(m) \gtreqless 1) = \sum_{s \in \mathcal{S}} \binom{N}{s} p^s (1-p)^{N-s} \\
  &\qquad\mbox{where}\quad \mathcal{S} = \left\{ s : \frac{p(0 \mid y, \nu, m, s, N)}{p(0 \mid y, \nl, m, s, N)} \lesseqgtr 1 \cap \frac{p(m \mid y, \nu, m, s, N)}{p(m \mid y, \nl, m, s, N)} \gtreqless 1 \right\}
\end{align*}

@@

Note that all these analyses are for evaluation of a single fixed time point at which $\lRsys(\cdot)$ or $\uRsys(\cdot)$ is computed.  Of relevance to the overall compute time is the behaviour over time, and it seems unlikely that the worst case scenario will occur for long runs of the times under analysis.

\subsection{Theoretical analysis for brake system example}
\label{ap:needtoopt-brake}

By way of example, a temporal analysis of the constrained worst case analysis is now presented for the real example in Section~\ref{sec:brakeex}.
%
%Figure \ref{fig:need-to-opt-8} shows the changing worst case probability (subject to $|y-p|>0.1$) that optimisation will be required over time for the actual choice of prior and the values of $m, N, \nu$ and $\nl$ in the brake example from the main body of the paper.  Note in particular that when $m=1$, Lemma 3 always applies for $y \in (0,1)$ and so optimisation is never required.  This is true for all values of $N$ and $y$.
As noted in Section~\ref{sec:brakeex}, the grid contained 301 time points and the system has 4 types of components,
meaning stochastic dominance must be verified via theory or optimisation $1,204$ times for each of $\lRsys(\cdot)$ and $\uRsys(\cdot)$.

Figure~\ref{fig:need-to-opt-8} shows the worst case probabilities (subject to $|y-p|>0.1$)
as they change over time in the brake example from the main body of the paper.
Displayed are the worst case probabilities that optimisation will be required for the choice of prior and the values of $m$ and $N$
as in Section~\ref{sec:brakeex}, but without using the test data (which define $s$).
Note in particular that when $m=1$ (as is the case for component types M and H),
Lemma 3 always applies for $y \in (0,1)$ and so optimisation is never required.
This is true for all values of $N$ and $y$.

@@

For the test data as used in Section~\ref{sec:brakeex},
theory could not determine stochastic dominance in 98 (or 8.1\%) of cases for $\lRsys(\cdot)$,
while it was in 52 (or 4.3\%) of cases for $\uRsys(\cdot)$.
